\documentclass[12pt]{article}
% \usepackage[left=0.5cm, right=0.5cm, top=0.5cm, bottom=0.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{tkz-euclide}
\usepackage{tikz}
\usepackage{changepage}
\usepackage{lipsum}
\usepackage{tree-dvips}
\usepackage{qtree}
\usepackage[linguistics]{forest}
\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{blindtext}
% \usepackage[cal=esstix,frak=euler,scr=boondox,bb= pazo]{mathalfa}
% the following 2 packages are used for changing the font. 
% \usepackage{mathptmx}
% \usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{multicol}
\graphicspath{{./images/}}
\allowdisplaybreaks
\allowbreak
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheoremstyle{named}{}{}{\itshape}{}{\bfseries}{.}{.5em}{\thmnote{#3's }#1}
\theoremstyle{named}
\newtheorem*{namedconjecture}{Distinct Factorizations Conjecture}
\newtheorem{conjecture}{Conjecture}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\arcsec}{arcsec}
\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\curl}{curl}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\id}{id}
\newcounter{customDef}
\renewcommand{\thecustomDef}{\arabic{customDef}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}

% the following line is for the omission of the title
\pagestyle{empty}
\begin{document}

\begin{enumerate}
    \item
    \begin{enumerate}
        \item $z=1 + \left(\cos\left(\frac{\pi k}{8} + i\sin\left(\frac{\pi k}{8}\right)\right)\right)$ for $k=0,1,2,3$. 
        \item $\exp(3\log 2 - \frac{\pi}{2} + i(\frac{3\pi}{2} + \log 2))$. 
        \item 0. 
    \end{enumerate}
    \item True; first use definition of uniform convergence, then with upper-bound considerations, use ratio test to see $\sum \frac{\sqrt{n} \cdot 2^n}{n!}$ converges absolutely on $\overline{D_2(0)}$. By Cauchy Criterion for infinite, series, the result follows. 
    \item 
    \begin{enumerate}
        \item Not entire; write $u(x,y) = x^2 + y^2$ and $v(x,y) = 0$ and look at the Cauchy-Riemann equations. 
        \item Not entire; Cauchy-Riemann equations are not satisfied. 
    \end{enumerate}
    \item
    \begin{enumerate}
        \item (DRAWINGS). 
        \item $S$ is compact; $S$ is bounded and closed, so by Heine-Borel, $S$ is compact. 
        \item Consider $f_M(z) = z + 3$, where $M = \begin{pmatrix}
            1 & 3 \\
            0 & 1
        \end{pmatrix}$ and $\det M = 1 \neq 0$. 
    \end{enumerate}
    \item $\frac{2\pi \cdot 16}{5}$. 
    \item Seek to use Louisville's theorem, but not sure on how to show that $|f|$ is bounded. 
    \item this follows from maximum modulus principle. 
    \item Use Rouche's theorem (try to use maximum modulus principle to show $|f(z)| < 1$ on the unit circle?). 
    \item Gamma function $(\Gamma)$? 
    \item $-\frac{\pi}{5}$ (hopefully my arithmetic is correct). 
\end{enumerate}

\end{document}